Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-06-26 PAPER/main.tex
bullet point abstract

\begin{comment}
\begin{abstract}
	\begin{itemize}
	\item ``first, alg for COP and show how used for single strip feasible arrangement''
	\item ``then go on to examine how alg can combine to tackle multi-strip version of problem - closely related to 1DBPP''
	\item discuss problems that arise
	\item variant/generalisation of the 1DBPP ``in which both the ordering and orientation of items in a container influences the validity and quality of a solution''
	\item ``problem that requires the cutting and socring of rectangular pieces of cardboard in the construction of boxes''
	\end{itemize}	
\end{abstract}
\end{comment}

@@

\section{Further Work}
\begin{itemize}
	\item \cite{miller1960}
	\item mffd+ items are packed one by one, could be a case where an items fits onto a strip but ahc cannot find a feasible solution, so item must be packed elsewhere, but if two new items could fit on the strip, ahc might be able to find a solution. 
	\item include item width in ahc, so add values to the blue edges of the graph, weighted edges, red edges have value = 0.
	\item Then the problem would be: find the minimum number of alternating cycles on $G$ such that the length of the cycle is less than or equal to some value $W$ (which is the strip width). The length of the cycle would be the sum of all the weighted edges, so the sum of all the blue edges, since red = 0. 
	\item then could break and form edges to create new components of different sizes if some are too large, or join together if some are small, thus decreasing the number of cycles
	\item or if possible, find a single alt Ham cycle, and break up into as few smaller cycles as possible such that the length of each cycle is less than or equal to $W$
	\item another way, create as few feasible subsets $\mathcal{I}' \subseteq \mathcal{I}$ such that the total width of the items in each subset $\mathcal{I}$ is less than $W$, i.e. perform usual FFD alg, ignore score widths
	\item then perform ahc on each set, try to find feasible solution.
	\item if sets dont have feasible solution, try swapping items between sets
	\item initial tests, Becker theorem 6 2015 paper 
\end{itemize}

>>>>

\begin{itemize}
	\item This paper addresses a generalisation of the one-dimensional bin-packing problem
	\item rectangular items scored to create/construct cardboard boxes
	\item items packed onto strips in order to be scored to aid construction of boxes
	\item 
	\item ``first, alg for COP and show how used for single strip feasible arrangement''
	\item ``then go on to examine how alg can combine to tackle multi-strip version of problem - closely related to 1DBPP''
	\item discuss problems that arise
	\item variant/generalisation of the 1DBPP ``in which both the ordering and orientation of items in a container influences the validity and quality of a solution''
	\item ``problem that requires the cutting and socring of rectangular pieces of cardboard in the construction of boxes''
\end{itemize}

@@

\section{Further Work}
\begin{itemize}
	\item \cite{miller1960}
	\item mffd+ items are packed one by one, could be a case where an items fits onto a strip but ahc cannot find a feasible solution, so item must be packed elsewhere, but if two new items could fit on the strip, ahc might be able to find a solution. 
	\item include item width in ahc, so add values to the blue edges of the graph, weighted edges, red edges have value = 0.
	\item Then the problem would be: find the minimum number of alternating cycles on $G$ such that the length of the cycle is less than or equal to some value $W$ (which is the strip width). The length of the cycle would be the sum of all the weighted edges, so the sum of all the blue edges, since red = 0. 
	\item then could break and form edges to create new components of different sizes if some are too large, or join together if some are small, thus decreasing the number of cycles
	\item or if possible, find a single alt Ham cycle, and break up into as few smaller cycles as possible such that the length of each cycle is less than or equal to $W$
	\item another way, create as few feasible subsets $\mathcal{I}' \subseteq \mathcal{I}$ such that the total width of the items in each subset $\mathcal{I}$ is less than $W$, i.e. perform usual FFD alg, ignore score widths
	\item then perform ahc on each set, try to find feasible solution.
	\item if sets dont have feasible solution, try swapping items between sets
	\item initial tests, Becker theorem 6 2015 paper \cite{garraffa2016}
	\item minimise waste on each strip, not just number of strips
	\item tsp return to base
\end{itemize}
